Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-07-24 analysis/paper/paper.Rmd
references rformat

---
title: "Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry"
author:
  - Wojciech Francuzik^1^
  - Sabine Dölle-Bierke^1^
  - Franziska Ruëff^2^ 
  - Claudia Pföhler^3^
  - Kathrin Scherer Hofmeier^4^
  - Margitta Worm^1^
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    #bookdown::html_document2:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
---

@@

**Highlights:**
  These are the highlights. 
**Document statistics:**
  Word count, figures, tables, references

@@

The factor most prominently associated with an increased risk of severe anaphylaxis was mastocytosis, and there were no differences in elicitor groups (Fig. \@ref(fig:figcofactors)). Mastocytosis was increasing the risk of cardiac arrest in patients undergoing IVA significantly more than in patients undergoing anaphylaxis due to other triggers (Fig. S\@ref(fig:cardiacmasto)).

@@

Baseline serum tryptase correlated with the severity of reactions in the Ring and Messmer scale and was more prominently increasing risk of severe anaphylaxis in IVA patients than in other cases (Fig. \@ref(fig:figcofactors)B).
Cases with cardiac arrest were associated with increased tryptase over eight ng/ml, and this proportion was higher in IVA when compared to other elicitors. Loss of consciousness was also associated with increased tryptase levels but only in patients with IVA (Fig. \@ref(fig:figcofactors)C). Based on the severity and symptom profile, we decided to use a tryptase cut off value of 8 ng/ml (Fig. S\@ref(fig:tryp2)) rather than the currently used 11.5 ng/ml.

>>>>

---
title: "Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry"
author:
  - Wojciech Francuzik^1^
  - Sabine Dölle-Bierke^1^
  - Franziska Ruëff^2^ 
  - Claudia Pföhler^3^
  - Kathrin Scherer Hofmeier^4^
  - Margitta Worm^1^
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    #bookdown::html_document2:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/expert-review-of-clinical-immunology.csl" # Insert path for the bib-style
---

@@

<!-- **Highlights:** -->
<!--   These are the highlights.  -->
**Document statistics:**
  Word count, figures, tables, references

@@

The factor most prominently associated with an increased risk of severe anaphylaxis was mastocytosis, and there were no differences in elicitor groups (Fig. \@ref(fig:figcofactors)). Mastocytosis was increasing the risk of cardiac arrest in patients undergoing IVA significantly more than in patients undergoing anaphylaxis due to other triggers (Fig. S\@ref(fig:supplement)).

@@

Baseline serum tryptase correlated with the severity of reactions in the Ring and Messmer scale and was more prominently increasing risk of severe anaphylaxis in IVA patients than in other cases (Fig. \@ref(fig:figcofactors)B).
Cases with cardiac arrest were associated with increased tryptase over eight ng/ml, and this proportion was higher in IVA when compared to other elicitors. Loss of consciousness was also associated with increased tryptase levels but only in patients with IVA (Fig. \@ref(fig:figcofactors)C). Based on the severity and symptom profile, we decided to use a tryptase cut off value of 8 ng/ml (Fig. S\@ref(fig:figcofactors)B) rather than the currently used 11.5 ng/ml.
